\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-21 methodology.tex
some updates

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{img/extent_manager}
\caption{Internal components of the real Extent Manager in Azure Storage vNext.}
\label{fig:extentmanager}
\vspace{-3mm}
\end{figure*}

@@

// mocked engine for intercepting Extent Manager messages
class MockedNetEngine : NetworkEngine {
  public override void SendMessage(Socket s, Message msg) {
    // intercept and relay Extent Manager messages
    PSharpRuntime.Send(TestingDriver,
      new ExtentManagerMsgEvent(), s, msg);
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{Mocked network engine in vNext.}
\label{fig:enginecode}
\vspace{-2mm}
\end{figure}

@@

  // extent node failure logic
  [OnEvent(FailEvent, ProcessFailure)]
  void ProcessFailure() {
    // notifies the Extent Manager that this EN failed
    this.Send(ExtentManagerMachine, new ENMsgEvent(),
      new ExtentNodeDeletion(ExtentId));
    // notifies the monitor that this EN failed
    this.Monitor<RepairMonitor>(new ENFailedEvent(), this);
    this.Halt(); // terminate this P# machine
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{The modeled EN in vNext.}
\label{fig:mocked_en}
\vspace{-2mm}
\end{figure}

@@

@@

  // other test harness driving logic
  ...
  void InjectNodeFailure() {
    // nondeterministically choose an EN using P#
    var node = (MachineId)this.Nondet(ExtentNodes);    
    this.Send(node, new FailEvent()); // fail the chosen EN
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{The TestingDriver machine in vNext.}
\label{fig:testing_driver}
\vspace{-2mm}
\end{figure}

@@

Figure~\ref{fig:testing_driver} illustrates how \psharp can be used to inject a nondeterministic failure. \texttt{TestingDriver} can call the \texttt{InjectNodeFailure} method, which invokes the \psharp method \texttt{Nondet()} to nondeterministically choose an \texttt{ExtentNode} from the set of available \texttt{ExtentNode} machines. \texttt{TestingDriver} then sends the chosen machine a \texttt{FailEvent} event. The chosen \texttt{ExtentNode} handles this event (see Figure~\ref{fig:mocked_en}) by wrapping the \texttt{ExtentNodeDeletion} message, which is a failure notification, to the \texttt{ENMsgEvent} and sends it to the \texttt{ExtentManager} machine. \texttt{ExtentNodeDeletion} is the same message that is used by the real vNext for unit testing, which maximizes code re-use. Next, the chosen \texttt{ExtentNode} notifies the liveness monitor that an EN has failed. Finally, the chosen \texttt{ExtentNode} calls the \psharp method \texttt{Halt()}, which causes the machine to terminate. \psharp is able to not only enumerate interleavings of asynchronous event handlers, but also calls to \texttt{Nondet()}, and thus failure injections.

  [OnEvent(RepeatEvent, GenerateTimeTick)]
  void GenerateTimeTick() {
    // nondeterministic choice controlled by P#
    if (this.Nondet())
      this.Send(this.Target, new TimerTickEvent());
    this.Send(this, new RepeatEvent()); // loop
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{Modeling timer expiration using \psharp.}
\label{fig:mocked_timer}
\vspace{-2mm}
\end{figure}

@@

  // hot state: repairing
  [OnEvent(ExtentRepairedEvent, ProcessExtentRepaired)]
  hot state Repairing {
    void ProcessExtentRepaired() {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{The RepairMonitor liveness monitor.}
\label{fig:monitor}
\vspace{-2mm}
\end{figure}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{img/extent_manager}
\caption{Internal components of the real Extent Manager in Azure Storage vNext.}
\label{fig:extentmanager}
\vspace{-5mm}
\end{figure*}

@@

// mocked engine for intercepting Extent Manager messages
class MockedNetEngine : NetworkEngine {
  public override void SendMessage(Socket s, Message msg) {
    // intercept and relay Extent Manager messages
    PSharpRuntime.Send(TestingDriver,
      new ExtentManagerMsgEvent(), s, msg);
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{Mocked network engine in vNext.}
\label{fig:enginecode}
\vspace{-2mm}
\end{figure}

@@

  // extent node failure logic
  [OnEvent(FailEvent, ProcessFailure)]
  void ProcessFailure() {
    // notifies the Extent Manager that this EN failed
    this.Send(ExtentManagerMachine, new ENMsgEvent(),
      new ExtentNodeDeletion(ExtentId));
    // notifies the monitor that this EN failed
    this.Monitor<RepairMonitor>(new ENFailedEvent(), this);
    this.Halt(); // terminate this P# machine
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{The modeled EN in vNext.}
\label{fig:mocked_en}
\vspace{-2mm}
\end{figure}

@@

  [OnEvent(RepeatEvent, GenerateTimeTick)]
  void GenerateTimeTick() {
    // nondeterministic choice controlled by P#
    if (this.Nondet())
      this.Send(this.Target, new TimerTickEvent());
    this.Send(this, new RepeatEvent()); // loop
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{Modeling timer expiration using \psharp.}
\label{fig:mocked_timer}
\vspace{-2mm}
\end{figure}

@@

  // other test harness driving logic
  ...
  void InjectNodeFailure() {
    // nondeterministically choose an EN using P#
    var node = (MachineId)this.Nondet(ExtentNodes);    
    this.Send(node, new FailEvent()); // fail the chosen EN
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{The TestingDriver machine in vNext.}
\label{fig:testing_driver}
\vspace{-2mm}
\end{figure}

@@

Figure~\ref{fig:testing_driver} illustrates how \psharp can be used for injecting nondeterministic failures. The \texttt{TestingDriver} machine can invoke the \psharp method \texttt{Nondet()} to nondeterministically choose an \texttt{ExtentNode} from the set of all available \texttt{ExtentNode}machines. Let $n_f$ be this chosen machine. \texttt{TestingDriver} can emulate a failure by sending $n_f$ a \texttt{FailEvent} event. The $n_f$ machine handles this event by wrapping the \texttt{ExtentNodeDeletion} message, which is a failure notification, to the \texttt{ENMsgEvent} and sending it to the \texttt{ExtentManager} machine (see Figure~\ref{fig:mocked_en}). \texttt{ExtentNodeDeletion} is the same message that is used by the real vNext for unit testing, which maximizes code re-use. Next, $n_f$ notifies the liveness monitor that it has failed. Finally, $n_f$ calls the \psharp method \texttt{Halt()}, which causes $n_f$ to terminate. \psharp is able to not only enumerate interleavings of asynchronous event handlers, but also calls to \texttt{Nondet()}, and thus failure injections.

@@

  // hot state: repairing
  [OnEvent(ExtentRepairedEvent, ProcessExtentRepaired)]
  hot state Repairing {
    void ProcessExtentRepaired() {
      var node = GetExtentNode(this.Payload);
      ExtentNode2Replica[node] = true;
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        goto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{The RepairMonitor liveness monitor.}
\label{fig:monitor}
\vspace{-2mm}
\end{figure}
